Rembrant

### 2024-07-01 script/breast_cancer/breast_description.Rmd
add markdown report for github

---
title: "Breast cancer"
author: "TF"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    number_sections: FALSE
    fig_caption: TRUE
    table_caption: TRUE
---

>>>>

---
title: "Breast cancer"
author: "TF"
output: 
  bookdown::html_document2:
    keep_md: true
    toc: yes
    toc_float: true
    number_sections: FALSE
    fig_caption: TRUE
    table_caption: TRUE
---

### 2024-07-01 script/rembrandt/rembrant_description.Rmd
add markdown report for github

---
title: "Rembrant"
author: "TF"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    number_sections: FALSE
    fig_caption: TRUE
    table_caption: TRUE
---

>>>>

---
title: "Rembrant"
author: "TF"
output: 
  bookdown::html_document2:
    keep_md: true
    toc: yes
    toc_float: true
    number_sections: FALSE
    fig_caption: TRUE
    table_caption: TRUE
---
